Assignment 4

### 2015-03-05 rmtw/a4/latex8.tex
Added chi test for #3

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}

@@

%Deficiencies introduction model

​\Section{Introduction}
Software inspections have since its inception [1] more than
25 years ago spawned quite some interest both from the
research community and industrial practice. The research
includes changes to the inspection process, e.g. [2], support to
the process, e.g. [3] and empirical studies, e.g. [4]. The
suggested improvements include active design reviews [5] and
perspective-based reading [6]. Industry has studied the
benefits of conducting software inspections [7].
The objective of this study is to compare and hence
evaluate how well the use-case based reading performs in
comparison to other methods. The study presents a controlled
experiment where use-case based reading is compared to
checklist-based reading.

\Section{Purpose of the Study}
* Purpose statement (copy paste from the file ‘Experiment\_Design.pdf’ file)

* Research Questions (copy paste from the file ‘Experiment\_Design.pdf’ file)

* Hypothesis (copy paste from the file ‘Experiment\_Design.pdf’ file)

@@

\Section{Results}
Read \url{https://dl.dropboxusercontent.com/u/2437798/Juristo%20Basics%20of%20Software%20Engineering%20Experimentation.pdf} pp. 133

@@

\bibliographystyle{latex8}
\bibliography{latex8}

>>>>

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}
\usepackage{verbatim}

@@

@@

\Section{Results}

@@

\Section{Tests for eff}

\verbatiminput{f_eff.txt}

Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.

\verbatiminput{t_eff.txt}

According to the test, the efficiency of CL is 7.3 while the efficiency of UC is 6.16 and H0 eff is therefore rejected.

\Section{Tests for rate}

\verbatiminput{f_rate.txt}

Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.

\verbatiminput{t_rate.txt}

According to the test, the rate of CL is 1.45 while the effectiveness of UC is 0.12 and h0 rate is therefore rejected.

\Section{Tests for #3}

%%R output
	Chi-squared test for given probabilities

data:  ct
X-squared = 5.4847, df = 2, p-value = 0.06442

Since our significance level is 0.05 and p > 0.05, there is no significant difference and h1 is rejected. 
%%R output

Chi-square test requirements[edit]
Quantitative data.
One or more categories.
Independent observations.
Adequate sample size (at least 10).
Simple random sample.
Data in frequency form.
All observations must be used.
\bibliographystyle{latex8}
\bibliography{latex8}
